Elaboration with First-Class Implicit Function Types

### 2020-02-28 paper.tex
stuff

\subsection{Related Works}
MLF \cite{le2014mlf} is an extension of System F with polymorphic subtyping
bounds, which supports strong inference for first class polymorphism. HML
\cite{leijen2009flexible}) is a simplified variant of MLF. Since these systems
diverge markedly from (fragments of) Martin-Löf type theory and rely critically
on subtyping, it is unclear how they could be extended to dependent type
theories. HMF \cite{leijen2008hmf} is a relatively simple system with
first-class polymorphism; however, it is also weaker than others in terms of
inferable annotations, and its more powerful variant (extended with n-ary
application handling) jumps in complexity.

@@

Some general comments on the comparison of FCIF to prior works. First, FCIF
supports dependent types and prior solutions do not. It is also unclear whether
prior solutions can scale to dependent types. In particular, QL's preprocessing
step is not applicable, since in a dependently typed spine we cannot do anything
with later arguments until previous arguments are actually elaborated, or else
it has to be restricted to non-dependent spines.

>>>>

\subsection{Related Works}
MLF \cite{le2014mlf} is an extension of System F with polymorphic subtyping
bounds, which supports strong inference for first class polymorphism. HML
\cite{leijen2009flexible}) is a simplified variant of MLF. Since these systems
diverge markedly from (fragments of) Martin-Löf type theory and rely critically
on subtyping, it is unclear how they could be extended to dependent type
theories. HMF \cite{leijen2008hmf} is a relatively simple system with
first-class polymorphism; however, it is also weaker than others in terms of
inferable annotations, and its more powerful variant (extended with n-ary
application handling) is more complex.

@@

Some general comments on the comparison of FCIF to prior works. First, FCIF
supports dependent types and prior solutions do not. It is also unclear whether
prior solutions can scale to dependent types. MLF and HML rely on subtyping, and
solutions which work one neutral spine at a time (HMF, GI, QL) also face issues
with dependently typed spines, since it is not possible to do anything with
later arguments in such spines until previous arguments are elaborated.
